A Survey of Near-Term Exoskeleton Technology\\ (Draft 4.0)

### 2015-09-30 technology.tex
more updates

\title{A Survey of Near-Term Exoskeleton Technology\\
(Draft 3.0)}

@@

Executive Summary to be written.

@@

This paper surveys near-term exoskeleton technology with an
emphasis on control.
A companion paper surveys implemented exoskeleton technology [survey.pdf].

@@

A later white paper could discuss the use of propulsive forces other
than foot contacts, as well as additional actuation at the contacts (air
bags, springs, other ways to rapidly apply stored energy) for
operator safety (dodging threats, ...) and high performance (jumping, ...).

@@

A future white paper could discuss the addition of extra limbs and
other effectors to an exoskeleton~\cite{IEEE07139896}.

@@

{\it Dennis E. Anderson, Michael L. Madigan, Maury A. Nussbaum,
“Maximum voluntary joint torque as a function of joint angle and
angular velocity: Model development and application to the lower
limb”, Journal of Biomechanics, 2007, Volume. 40, Issue 14, Pages
3105-3113} says max knee torque is around 350Nm. They only consider
max knee angular velocities around 2revolutions/second.

@@

However, on the Atlas robot differential oil pressure is used
to estimate actuator force, as this form of force sensing
is quite mechanically robust (low maintenance).
This measurement is before the piston
seals and transmission, so it does not capture those sources
of friction. The joint torques are off by up to 10Nm at each joint.
The Sarcos robot uses load cells in the actuator to joint transmissions.

@@

Simple attachements of a linear actuator to a rotary joint lead to
a sinusoidal dependence of the moment arm on the joint angle.
The moment arm can be made more constant or programmed with
a different dependence of moment arm on angle (a static gear shift)
by using multi-bar transmissions,
or by using tendon attachments with antagonistic actuators.
Note that the actuators do not need to be symmetric.
Gear shifts and variable transmissions would allow the maximum torque
and maximum no-load speed of the joint to be increased (also true
for all other actuation types).

@@

The water cooled motor driver they developed is capable of 80V and
80A continuous.~\cite{IEEE05649683}

They modified
MAXON EC-powermax30 200W brush-less motors, and added harmonic drives
to make an integrated actuator.
The maximum speed of these actuators was 3 revolutions/second.
The maximum torque using 2 drivers/motor was theoretically 400Nm, but
we have only seen 300Nm in the published data. 2 rev/s can be achieved
at peak torque (Fig~\ref{f:s1}).~\cite{IEEE05649683}

@@

Peak currents are in the range of 100-150A.
{\it
``High current load on Li-ion or Ni-MH batteries affects life
span or cause damage. They cannot be charged with high
current rate. Electrical double layer capacitors are suitable for
such instantaneous current supply because they can supply
high current without degradation for high current while
their power capacity is not large. Capacitors can be charged
with high current. Combination of an electrical double layer
capacitor and battery is adopted. The robot carries a capacitor
developed for it by Shizuki Electric Co. Inc. Specifications of
the developed capacitor are shown in Tab.II.''}~\cite{IEEE05649683}
Note that this capacitor weighs 9 kg (Fig~\ref{f:s2}).

@@

We don't know whether these actuators can be made backdrivable with
high performance torque control. Pre-Schaft, the researchers were exploring
nonlinear series elastic actuation (big springs)
to help handle impacts and large force
transients~\cite{IEEE06651562}.

@@

Can we use local energy storage to assist control: charging batteries or
supercapacitors, pressurizing accumulators, using springs, ... ?
The reference electrical design used a big capacitor to help handle
peak loads. We believe that many behaviors ``slosh'' potential and
kinetic energy back and forth.
Running exchanges vertical velocity and energy storage in spring-like
tissue.
Walking exchanges forward velocity and gravitational storage.
We also believe that energy storage can be used to start and stop
highly dynamic transient behaviors.
Jumping stilts and pogo sticks are an excellent demonstration
of the use of energy storage to enhance human
capabilities.
\url{https://www.youtube.com/watch?v=lbp41vWP4o4},
\url{https://www.youtube.com/watch?v=9ZOd7yEyhwI}

In addition, physical springs protect the exoskeleton from damage
and contribute to system dependability.
The JST lab was exploring human-scale jumping robots
with 
nonlinear series elastic actuation (big springs)
to help handle impacts and large force
transients~\cite{IEEE06651562}.

@@

Energy storage and actuation for superhuman manueverability.
\url{http://www.ric.org/app/files/public/4898/LemusVallery_GyroscopicBackpack_EMBC2014pdf.pdf}
\url{http://www.ncbi.nlm.nih.gov/pubmed/22169384}

@@

Several labs have explored using the piston of an internal combustion
engine as a stand-alone linear or rotary actuator. In this case
the combustion event would be carefully metered and timed. Repetitive
combustion events combined with mechanical filtering could lead to smooth
output forces. This approach inherits the desirable energy storage capacity
of liquid fuels. 
\url{http://softroboticstoolkit.com/book/combustion-driven-actuators}
\url{http://www.nature.com/articles/srep04296}
\url{http://arxiv.org/abs/1402.7101}
\url{http://ntrs.nasa.gov/archive/nasa/casi.ntrs.nasa.gov/20100021938.pdf}
% https://smartech.gatech.edu/bitstream/handle/1853/19873/warta_brett_j_200712_mast.pdf
\url{http://www.msoe.edu/servlet/JiveServlet/previewBody/5589-102-1-7785/Sarah_Swanson_Final_Paper.pdf}

@@

Different types of actuation can be combined: springs and electric motors,
for example. This combination can also be viewed as combining energy
storage and actuation. Slow pneumatics and fast electric motors~\cite{Morimoto,UCLA}.
Mini/Macro~\cite{Stanford}. In this view, the human operator is just
one more set of actuators to be added to the combined system.

@@

Examples:~\cite{IEEE07222598}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.75\textwidth]{figs/shc1}
\caption{From xxx}
\label{f:hip-knee}
\end{figure}

@@

\bibliographystyle{plain}
\bibliography{exo}

>>>>

\title{A Survey of Near-Term Exoskeleton Technology\\
(Draft 4.0)}

@@

\begin{enumerate}
\item
We recommend the exploration of how to implement and utilize practical
{\bf gear shifts and clutches} (or equivalents).
\item
We recommend exploring the combination of {\bf passive energy storage}
(springs, etc.) with active actuation.
\item
We recommend the exploration of {\bf hybrid actuation,} where strong but 
slow actuators are combined with fast but weak actuators.
\item
We recommend the exploration of {\bf multi-joint actuation}.
\item
We recommend applying {\bf as many sensors as possible,} and asking the performers
to make it easy to add more by making the sensor network available in the design.
\end{enumerate}

@@

This paper surveys near-term exoskeleton technology with an
emphasis on control.
A companion paper surveys implemented exoskeleton technology.\\
\url{http://www.cs.cmu.edu/~cga/exo/survey.pdf}

@@

A future white paper could discuss the use of propulsive forces other
than foot contacts, as well as additional actuation at the contacts (air
bags, springs, other ways to rapidly apply stored energy) for
operator safety (dodging threats, ...) and high performance (jumping, ...).

@@

A future white paper could discuss the addition of extra limbs and
other effectors to an exoskeleton.\\
\url{http://ieeexplore.ieee.org/xpl/login.jsp?tp=&arnumber=7139896}\\

@@

{\it Dennis E. Anderson, Michael L. Madigan, Maury A. Nussbaum,
“Maximum voluntary joint torque as a function of joint angle and
angular velocity: Model development and application to the lower
limb”, Journal of Biomechanics, 2007, Volume. 40, Issue 14, Pages
3105-3113} says max knee torque is around 350Nm. They only consider
max knee angular velocities around 2revolutions/second.\\
\url{http://www.cs.cmu.edu/~cga/exo/info/Anderson2007.pdf}

Another useful specification is the cost in torque output and power
of exoskeleton and payload mass if the exoskeleton runs like a human.
Note that the speed requirements on the exoskeleton do not change as
payload increases.
\begin{itemize}
\item
hip: 2Nm/kg, 13W/kg
\item
knee 1.5Nm/kg, knee 6W/kg
\item
ankle 2Nm/kg, 13W/kg
\end{itemize}
From: {\it The biomechanics of running,} Tom F. Novacheck,
Gait and Posture 7 (1998) 77–95.

@@

However, on the Atlas robot differential oil pressure is used
to estimate actuator force, as this form of force sensing
is quite mechanically robust (low maintenance).
This measurement is before the piston
seals and transmission, so it does not capture these sources
of friction. The joint torques are off by up to 10Nm at each joint.
The Sarcos robot uses load cells in the actuator to joint transmissions.

@@

Simple attachments of a linear actuator to a rotary joint lead to
a sinusoidal dependence of the moment arm on the joint angle.
The moment arm can be made more constant or programmed with
a different dependence of moment arm on angle (a static gear shift)
by using multi-bar transmissions,
or by using tendon attachments with antagonistic actuators.
Note that the actuators do not need to be symmetric.
Gear shifts and variable transmissions would allow the maximum torque
and maximum no-load speed of the joint to be increased (also true
for all other actuation types).

@@

The water cooled motor driver they developed is capable of 80V and
80A continuous.\\
\url{http://ieeexplore.ieee.org/xpl/login.jsp?tp=&arnumber=5649683}\\

They modified
MAXON EC-powermax30 200W brush-less motors, and added harmonic drives
to make an integrated actuator.
The maximum speed of these actuators was 3 revolutions/second.
The maximum torque using 2 drivers/motor was theoretically 400Nm, but
we have only seen 300Nm in the published data. 2 rev/s can be achieved
at peak torque (Fig~\ref{f:s1}).\\
\url{http://ieeexplore.ieee.org/xpl/login.jsp?tp=&arnumber=5649683}\\

@@

Peak currents are in the range of 100-150A.
{\it
``High current load on Li-ion or Ni-MH batteries affects life
span or cause damage. They cannot be charged with high
current rate. Electrical double layer capacitors are suitable for
such instantaneous current supply because they can supply
high current without degradation for high current while
their power capacity is not large. Capacitors can be charged
with high current. Combination of an electrical double layer
capacitor and battery is adopted. The robot carries a capacitor
developed for it by Shizuki Electric Co. Inc. Specifications of
the developed capacitor are shown in Tab.II.''}\\
\url{http://ieeexplore.ieee.org/xpl/login.jsp?tp=&arnumber=5649683}\\
Note that this capacitor weighs 9 kg (Fig~\ref{f:s2}).

@@

We don't know whether these actuators can be made backdrivable with
high performance torque control. Pre-Schaft, the researchers were exploring
nonlinear series elastic actuation (big springs)
to help handle impacts and large force
transients.\\
\url{http://ieeexplore.ieee.org/xpl/login.jsp?tp=&arnumber=6651562}\\

@@

Can we use local energy storage to assist control: charging batteries or
supercapacitors, pressurizing accumulators, using springs, ... ?
The reference electrical design used a big capacitor to help handle
peak loads. We believe that many behaviors ``slosh'' potential and
kinetic energy back and forth.
Running exchanges vertical velocity and energy storage in spring-like
tissue.
Walking exchanges forward velocity and gravitational storage.
We also believe that energy storage can be used to start and stop
highly dynamic transient behaviors.
Jumping stilts and pogo sticks are an excellent demonstration
of the use of energy storage to enhance human
capabilities.\\
\url{https://www.youtube.com/watch?v=lbp41vWP4o4},\\
\url{https://www.youtube.com/watch?v=9ZOd7yEyhwI}

In addition, physical springs protect the exoskeleton from damage
and contribute to system dependability.
The JST lab was exploring human-scale jumping robots
with 
nonlinear series elastic actuation (big springs)
to help handle impacts and large force
transients.\\
\url{http://ieeexplore.ieee.org/xpl/login.jsp?tp=&arnumber=6651562}\\

@@

Energy storage and actuation for superhuman manueverability.\\
\url{http://www.ncbi.nlm.nih.gov/pubmed/22169384}\\
\url{http://www.ric.org/app/files/public/4898/LemusVallery_GyroscopicBackpack_EMBC2014pdf.pdf}

@@

Several labs have explored using the piston of an internal combustion
engine as a stand-alone linear or rotary actuator. In this case
the combustion event would be carefully metered and timed. Repetitive
combustion events combined with mechanical filtering could lead to smooth
output forces. This approach inherits the desirable energy storage capacity
of liquid fuels.\\ 
\url{http://softroboticstoolkit.com/book/combustion-driven-actuators}\\
\url{http://www.nature.com/articles/srep04296}\\
\url{http://arxiv.org/abs/1402.7101}\\
\url{http://ntrs.nasa.gov/archive/nasa/casi.ntrs.nasa.gov/20100021938.pdf}\\
% https://smartech.gatech.edu/bitstream/handle/1853/19873/warta_brett_j_200712_mast.pdf
\url{http://www.msoe.edu/servlet/JiveServlet/previewBody/5589-102-1-7785/Sarah_Swanson_Final_Paper.pdf}

@@

Different types of actuation can be combined: springs and electric motors,
for example. This combination can also be viewed as combining energy
storage and actuation. Slow pneumatics and fast electric motors.\\
\url{http://www.cs.cmu.edu/~cga/exo/survey.pdf}\\
Mini/Macro.\\
\url{http://ieeexplore.ieee.org/xpl/login.jsp?tp=&arnumber=4479941}\\
In this view, the human operator is just
one more set of actuators to be added to the combined system.

@@

Examples:\\
\url{http://ieeexplore.ieee.org/xpl/login.jsp?tp=&arnumber=7222598}\\

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.75\textwidth]{figs/shc1}
\caption{From {\it The biomechanics of running,}
Tom F. Novacheck,
Gait and Posture 7 (1998) 77–95.}
\label{f:hip-knee}
\end{figure}

@@

%\bibliographystyle{plain}
%\bibliography{exo}
